---
title: "Gun Control Chi Square"
author: "Max Russer"
date: "November 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I am Max and I am adding some text here to see whats up. 


Its Max again, and Im updating text. 

Hey its Juan
WTF IS THIS WORKING OR WHAT
TF

```{r}
library(tidyverse)

gc_df <- read_csv("gc_df.csv")

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender) 

rownames(get_guns) <- c("Female", "Male")


```

I am the collaborator (Max) and I am going to do chi-square

Is there a significant difference in gun control persepectives (as related to access to guns) for males and females?

Is there a significant association between sex and gun control recommendations?

Is perception of gun control access independent of sex?

Chi-Square
```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1)

guns_prop

# Performing chi-square 

# Show table and table of proportions for chi-square 

guns_x2 <- chisq.test(get_guns)
guns_x2

```

Recommended government action on gun access differs significantly for males and females ($\chi^2$(`r guns_c2$parameter`) = p < 0.001)
